### 2018-01-25 thermocouple/paper.tex
added circuit diagram
Intro

	Introduction goes here

@@

	Observations go here

>>>>

	Thermocouples convert a temperature difference into an electromotive force (EMF), and are made of two wires of dissimilar metals which are joined at each end. The wires in a temperature gradient will allow the free carriers at the hot end have more kinetic energy and tend to diffuse towards the cold end, which will in turn create an electric field which has a averse tendency the heat flow. In this experiment, the temperature difference is measure of an ice bath which stays at constant temperature, and another body of water with temperature which will vary.

@@

	Observations
